Possible Inconsistency in Maximum Likelihood Calculation of Ancestral States

### 2017-05-02 joint_inf.tex
text in appendix and figures

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
\multicolumn{3}{c}{Classical}\\
    \hline
$\siteSplit_j$   &$P(\siteSplitRV=\siteSplit_j \mid \tau_1,t^*)$&$P(\siteSplitRV=\siteSplit_j \mid \tau_2,t^*)$\\
    \hline
    $\emptyset$    &$1+x^2+y^2+4xy^2+x^2y^2$&$1+2xy+2xy^2+x^2y+y^3+x^2y^2$\\
    $\{1\}$        &$1-x^2+y^2-x^2y^2$&$1-x^2y+y^3-x^2y^2$\\
    $\{2\}$        &$1+x^2-y^2-x^2y^2$&$1+x^2y-y^3-x^2y^2$\\
    $\{3\}$        &$1-x^2+y^2-x^2y^2$&$1-x^2y+y^3-x^2y^2$\\
    $\{1,2\}$      &$1-x^2-y^2+x^2y^2$&$1+2xy-2xy^2-x^2y-y^3+x^2y^2$\\
    $\{1,3\}$      &$1+x^2+y^2-4xy^2+x^2y^2$&$1-2xy-2xy^2+x^2y+y^3+x^2y^2$\\
    $\{2,3\}$      &$1-x^2-y^2+x^2y^2$&$1-2xy+2xy^2-x^2y-y^3+x^2y^2$\\
    $\{1,2,3\}$    &$1+x^2-y^2-x^2y^2$&$1+x^2y-y^3-x^2y^2$\\
    \hline
\multicolumn{3}{c}{Modified}\\
    \hline
$\siteSplit_j$   &$P(\siteSplitRV=\siteSplit_j \mid \tau_1,t)$&$P(\siteSplitRV=\siteSplit_j \mid \tau_2,t)$\\
    \hline
    $\emptyset$     &$1+x'^2+y'^2+4x'y'w'+x'^2y'^2$&$1+2x'y'+2x'y'w'+x'^2w'+y'^2w'+x'^2y'^2$\\
    $\{1\}$        &$1-x'^2+y'^2-x'^2y'^2$&$1-x'^2w'+y'^2w'-x'^2y'^2$\\
    $\{2\}$        &$1+x'^2-y'^2-x'^2y'^2$&$1+x'^2w'-y'^2w'-x'^2y'^2$\\
    $\{3\}$        &$1-x'^2+y'^2-x'^2y'^2$&$1-x'^2w'+y'^2w'-x'^2y'^2$\\
    $\{1,2\}$      &$1-x'^2-y'^2+x'^2y'^2$&$1+2x'y'-2x'y'w'-x'^2w'-y'^2w'+x'^2y'^2$\\
    $\{1,3\}$      &$1+x'^2+y'^2-4x'y'w'+x'^2y'^2$&$1-2x'y'-2x'y'w'+x'^2w'+y'^2w'+x'^2y'^2$\\
    $\{2,3\}$      &$1-x'^2-y'^2+x'^2y'^2$&$1-2x'y'+2x'y'w'-x'^2w'-y'^2w'+x'^2y'^2$\\
    $\{1,2,3\}$    &$1+x'^2-y'^2-x'^2y'^2$&$1+x'^2w'-y'^2w'-x'^2y'^2$\\
    \hline
\end{tabular}
\caption{Site pattern probabilities.
All values are multiplied by $1/8$.}
\label{tab:sitepatprob}
\end{table}

\begin{table}
\centering
\begin{tabular}{|l|ll|}
    \multicolumn{3}{c}{$\tau=\tau_1$}\\
    \hline
    $\siteSplit_j$    & $\ancestralSplitPartition_j(\tau, t)$ & $P(\ancestralSplitRV=\xi_j \mid \siteSplitRV=\siteSplit_j,\tau,t)$\\
    \hline
    $\emptyset$&
    $\emptyset$&
    $(1+x)^2   (1+w)(1+y)^2$\\
     $\{1\}$    &
    $\emptyset$&
    $(1+x)(1-x)(1+w)(1+y)^2$\\
     $\{2\}$    &
    $\emptyset$&
    $(1+x)^2   (1+w)(1+y)(1-y)$\\
     $\{3\}$    &
    $\emptyset$&
    $(1+x)(1-x)(1+w)(1+y)^2$\\
    $\{1,2\}$  &
    $\{\emptyset,\{1,2,3\}\}$&
    $(1+x)(1-x)(1+w)(1+y)(1-y)$\\
    $\{1,3\}$  &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{2\}\\
                    \{1,2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)^2   (1+w)(1-y)^2\\
                    (1+x)^2   (1-w)(1+y)^2\\
                    (1-x)^2   (1+w)(1+y)^2
                \end{array}$\\
    $\{2,3\}$  &
                $\{\emptyset,\{1,2,3\}\}$&
                $(1+x)(1-x)(1+w)(1+y)(1-y)$\\
    $\{1,2,3\}$&
                $\emptyset$&
                $(1+x)^2   (1+w)(1+y)(1-y)$\\
    \hline
    \multicolumn{3}{c}{$\tau=\tau_2$}\\
    \hline
    $\siteSplit_j$    & $\ancestralSplitPartition_j(\tau, t)$ & $P(\ancestralSplitRV=\xi_j \mid \siteSplitRV=\siteSplit_j,\tau,t)$\\
    \hline
    $\emptyset$       &$\emptyset$&$(1+x)^2   (1+w)(1+y)^2$\\
    $\{1\}$          &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{1\}
                \end{array}\right.$&
    $\begin{array}{l}
                        (1+x)(1-x)(1+w)(1+y)^2\\
                        (1+x)^2   (1-w)(1+y)(1-y)
                    \end{array}$\\
      $\{2\}$          &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{1\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)^2   (1+w)(1+y)(1-y)\\
                    (1+x)(1-x)(1-w)(1+y)^2
                    \end{array}$\\
      $\{3\}$          &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)(1-x)(1+w)(1+y)^2\\
                    (1+x)^2   (1-w)(1+y)(1-y)
                    \end{array}$\\
     $\{1,2\}$         &
    $\left\{\begin{array}{l}
                    \{\emptyset,\{1,2\}\}\\
                    \{2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)(1-x)(1+w)(1+y)(1-y)\\
                    (1+x)^2   (1-w)(1+y)^2
                    \end{array}$\\
     $\{1,3\}$         &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{\{1\},\{2\}\}\\
                    \{1,2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)^2   (1+w)(1-y)^2\\
                    (1+x)(1-x)(1-w)(1+y)(1-y)\\
                    (1-x)^2   (1+w)(1+y)^2
                    \end{array}$\\
      $\{2,3\}$        &
    $\left\{\begin{array}{l}
                    \{\emptyset,\{1,2\}\}\\
                    \{1\}\\
                    \{2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)(1-x)(1+w)(1+y)(1-y)\\
                    (1-x)^2   (1-w)(1+y)^2\\
                    (1+x)^2   (1-w)(1-y)^2
                    \end{array}$\\
     $\{1,2,3\}$       &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)^2   (1+w)(1+y)(1-y)\\
                    (1+x)(1-x)(1-w)(1+y)^2
                    \end{array}$\\
    \hline
\end{tabular}
\caption{Likelihood calculations for all site patterns and ancestral state partitions.
All values multiplied by $1/32$.
Likelihoods with multiple entries will have maxima determined by unknown branch length parameters.}
\label{tab:likelihoods}
\end{table}

@@

For compactness, define, e.g., $p_0 = P(\siteSplitRV=\emptyset \mid \tau=\tau_1,t=\{x,y,y\})$, keeping in mind it is a function of parameters $x,y$.

@@

We construct a similar lower bound on the Felsenstein partial likelihood.
Replace all $(1+w)$ terms with $(1-w)$ and focus just on the partial likelihood.
Then if $(1+x)(1-y) > (1-x)(1+y)$,
\begin{align*}
    \tilde{\ell}_{\tau_1,\{x,y,y\}}(\tau_2, \{x',y',w'\}; \fullAncestralSplitPartitions(\tau_2,\{x',y',w'\}))
    &=      p_{0}  \cdot\log((1+x')^2   (1+w')(1+y')^2) \\
    &\qquad + p_{1}  \cdot\log((1+x')^2   (1-w')(1+y')(1-y')) \\
    &\qquad + p_{2}  \cdot\log((1+x')^2   (1-w')(1+y')(1-y')) \\
    &\qquad + p_{3}  \cdot\log((1+x')^2   (1-w')(1+y')(1-y')) \\
    &\qquad + p_{12} \cdot\log((1+x')^2   (1-w')(1+y')^2) \\
    &\qquad + p_{123}\cdot\log((1+x')^2   (1-w')(1+y')(1-y'))\\
    &\qquad + p_{13} \cdot\log((1+x')^2   (1-w')(1-y')^2) \\
    &\qquad + p_{23} \cdot\log((1+x')^2   (1-w')(1-y')^2),
\end{align*}
otherwise
\begin{align*}
    \tilde{\ell}_{\tau_1,\{x,y,y\}}(\tau_2, \{x',y',w'\}; \fullAncestralSplitPartitions(\tau_2,\{x',y',w'\}))
    &=      p_{0}  \cdot\log((1+x')^2    (1+w')(1+y')^2) \\
    &\qquad + p_{1}  \cdot\log((1+x')(1-x')(1-w')(1+y')^2) \\
    &\qquad + p_{2}  \cdot\log((1+x')(1-x')(1-w')(1+y')^2) \\
    &\qquad + p_{3}  \cdot\log((1+x')(1-x')(1-w')(1+y')^2) \\
    &\qquad + p_{12} \cdot\log((1+x')^2    (1-w')(1+y')^2) \\
    &\qquad + p_{123}\cdot\log((1+x')(1-x')(1-w')(1+y')^2)\\
    &\qquad + p_{13} \cdot\log((1-x')^2    (1-w')(1+y')^2) \\
    &\qquad + p_{23} \cdot\log((1-x')^2    (1-w')(1+y')^2).
\end{align*}
Letting
$$
b = p_{1}+p_{2}+p_{3}+p_{123}
$$
yields
\begin{align*}
    \tilde{\ell}_{\tau_1,\{x,y,y\}}(\tau_2, \{x',y',w'\}; \fullAncestralSplitPartitions(\tau_2,\{x',y',w'\}))
    &=      2\cdot\log(1+x') \\
    &\qquad + (2-b)  \cdot\log(1+y') \\
    &\qquad + b      \cdot\log(1-y') \\
    &\qquad + p_{0}\cdot\log(1+w') \\
    &\qquad + (1-p_{0})\cdot\log(1-w')
\end{align*}
for the first lower bound, but, upon maximizing, we obtain the same value for both cases, namely
\begin{align*}
    \tilde{\ell}_{\tau_1,\{x,y,y\}}(\tau_2, \{x',y',w'\}; \fullAncestralSplitPartitions(\tau_2,\{x',y',w'\}))
    &=      2\cdot\log(2) \\
    &\qquad + (2-b)  \cdot\log(2-b) \\
    &\qquad + b      \cdot\log(b) \\
    &\qquad + p_{0}\cdot\log(2p_{0}) \\
    &\qquad + (1-p_{0})\cdot\log(2(1-p_{0}))
\end{align*}
maximized at $\{1,1-b,1-2p_{0}\}$.
Our lower bound is
\begin{align*}
    L_{\tau_1,\tau_2}(\mathbf{p}_{xy}) &:= \shannonDivergence_{\tau_1,\{x,y,y\}}(\tau_2,\{1,1-b,1-2p_{0}\}) \\
                                           &+ 2\cdot\log(2) + (2-b)  \cdot\log(2-b) + b      \cdot\log(b) + p_{0}\cdot\log(2p_{0}) + (1-p_{0})\cdot\log(2(1-p_{0})).
\end{align*}

@@

Ideally, we want the region where
$$
L_{\tau_1,\tau_2}(\mathbf{p}_{xy}) \ge \max(L^{1}_{\tau_1,\tau_1}(\mathbf{p}_{xy}), L^{2}_{\tau_1,\tau_1}(\mathbf{p}_{xy}),L^{3}_{\tau_1,\tau_1}(\mathbf{p}_{xy})).
$$
Currently being slightly lazy, I'm considering values for $\{x,y\}$ where all of
$$
L_{\tau_1,\tau_2}(\mathbf{p}_{xy}) \ge L^{1}_{\tau_1,\tau_1}(\mathbf{p}_{xy}),
$$
$$
L_{\tau_1,\tau_2}(\mathbf{p}_{xy}) \ge L^{2}_{\tau_1,\tau_1}(\mathbf{p}_{xy})
$$
and
$$
L_{\tau_1,\tau_2}(\mathbf{p}_{xy}) \ge L^{3}_{\tau_1,\tau_1}(\mathbf{p}_{xy})
$$
hold.
Since these are three inequalities in two variables, we can plot them analytically---see Fig.~\ref{fig:inconsistency-farris}.

@@

>>>>

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
    \hline
$\siteSplit_j$   &$P(\siteSplitRV=\siteSplit_j \mid \tau_1,t)$&$P(\siteSplitRV=\siteSplit_j \mid \tau_2,t)$\\
    \hline
    $\emptyset$    &$1+x'^2+y'^2+4x'y'w'+x'^2y'^2$&$1+2x'y'+2x'y'w'+x'^2w'+y'^2w'+x'^2y'^2$\\
    $\{1\}$        &$1-x'^2+y'^2-x'^2y'^2$&$1-x'^2w'+y'^2w'-x'^2y'^2$\\
    $\{2\}$        &$1+x'^2-y'^2-x'^2y'^2$&$1+x'^2w'-y'^2w'-x'^2y'^2$\\
    $\{3\}$        &$1-x'^2+y'^2-x'^2y'^2$&$1-x'^2w'+y'^2w'-x'^2y'^2$\\
    $\{1,2\}$      &$1-x'^2-y'^2+x'^2y'^2$&$1+2x'y'-2x'y'w'-x'^2w'-y'^2w'+x'^2y'^2$\\
    $\{1,3\}$      &$1+x'^2+y'^2-4x'y'w'+x'^2y'^2$&$1-2x'y'-2x'y'w'+x'^2w'+y'^2w'+x'^2y'^2$\\
    $\{2,3\}$      &$1-x'^2-y'^2+x'^2y'^2$&$1-2x'y'+2x'y'w'-x'^2w'-y'^2w'+x'^2y'^2$\\
    $\{1,2,3\}$    &$1+x'^2-y'^2-x'^2y'^2$&$1+x'^2w'-y'^2w'-x'^2y'^2$\\
    \hline
\end{tabular}
\caption{Site pattern probabilities.
All values are multiplied by $1/8$.}
\label{tab:sitepatprob}
\end{table}

\begin{table}
\centering
\begin{tabular}{|l|ll|}
    \multicolumn{3}{c}{$\tau=\tau_1$}\\
    \hline
    $\siteSplit_j$    & $\ancestralSplitPartition_j(\tau, t)$ & $P(\ancestralSplitRV=\xi_j \mid \siteSplitRV=\siteSplit_j,\tau,t)$\\
    \hline
    $\emptyset$&
    $\emptyset$&
    $(1+x)^2   (1+w)(1+y)^2$\\
     $\{1\}$    &
    $\emptyset$&
    $(1+x)(1-x)(1+w)(1+y)^2$\\
     $\{2\}$    &
    $\emptyset$&
    $(1+x)^2   (1+w)(1+y)(1-y)$\\
     $\{3\}$    &
    $\emptyset$&
    $(1+x)(1-x)(1+w)(1+y)^2$\\
    $\{1,2\}$  &
    $\{\emptyset,\{1,2,3\}\}$&
    $(1+x)(1-x)(1+w)(1+y)(1-y)$\\
    $\{1,3\}$  &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{2\}\\
                    \{1,2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)^2   (1+w)(1-y)^2\\
                    (1+x)^2   (1-w)(1+y)^2\\
                    (1-x)^2   (1+w)(1+y)^2
                \end{array}$\\
    $\{2,3\}$  &
                $\{\emptyset,\{1,2,3\}\}$&
                $(1+x)(1-x)(1+w)(1+y)(1-y)$\\
    $\{1,2,3\}$&
                $\emptyset$&
                $(1+x)^2   (1+w)(1+y)(1-y)$\\
    \hline
    \multicolumn{3}{c}{$\tau=\tau_2$}\\
    \hline
    $\siteSplit_j$    & $\ancestralSplitPartition_j(\tau, t)$ & $P(\ancestralSplitRV=\xi_j \mid \siteSplitRV=\siteSplit_j,\tau,t)$\\
    \hline
    $\emptyset$       &$\emptyset$&$(1+x)^2   (1+w)(1+y)^2$\\
    $\{1\}$          &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{1\}
                \end{array}\right.$&
    $\begin{array}{l}
                        (1+x)(1-x)(1+w)(1+y)^2\\
                        (1+x)^2   (1-w)(1+y)(1-y)
                    \end{array}$\\
      $\{2\}$          &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{1\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)^2   (1+w)(1+y)(1-y)\\
                    (1+x)(1-x)(1-w)(1+y)^2
                    \end{array}$\\
      $\{3\}$          &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)(1-x)(1+w)(1+y)^2\\
                    (1+x)^2   (1-w)(1+y)(1-y)
                    \end{array}$\\
     $\{1,2\}$         &
    $\left\{\begin{array}{l}
                    \{\emptyset,\{1,2\}\}\\
                    \{2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)(1-x)(1+w)(1+y)(1-y)\\
                    (1+x)^2   (1-w)(1+y)^2
                    \end{array}$\\
     $\{1,3\}$         &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{\{1\},\{2\}\}\\
                    \{1,2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)^2   (1+w)(1-y)^2\\
                    (1+x)(1-x)(1-w)(1+y)(1-y)\\
                    (1-x)^2   (1+w)(1+y)^2
                    \end{array}$\\
      $\{2,3\}$        &
    $\left\{\begin{array}{l}
                    \{\emptyset,\{1,2\}\}\\
                    \{1\}\\
                    \{2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)(1-x)(1+w)(1+y)(1-y)\\
                    (1-x)^2   (1-w)(1+y)^2\\
                    (1+x)^2   (1-w)(1-y)^2
                    \end{array}$\\
     $\{1,2,3\}$       &
    $\left\{\begin{array}{l}
                    \emptyset\\
                    \{2\}
                \end{array}\right.$&
    $\begin{array}{l}
                    (1+x)^2   (1+w)(1+y)(1-y)\\
                    (1+x)(1-x)(1-w)(1+y)^2
                    \end{array}$\\
    \hline
\end{tabular}
\caption{Likelihood calculations for all site patterns and ancestral state partitions.
All values multiplied by $1/32$.
Likelihoods with multiple entries will have maxima determined by unknown branch length parameters.
See Appendix for full calculations.}
\label{tab:likelihoods}
\end{table}

@@

For compactness, define
p_0 = P(\siteSplitRV=\emptyset \mid \tau=\tau_1,t=\{x,y,y\})
with similar definitions for the remaining generating probabilities.

@@

We construct a similar lower bound on the Felsenstein partial likelihood.
Replace all $(1+w)$ terms with $(1-w)$ and focus just on the partial likelihood.
Then if $(1+x)(1-y) > (1-x)(1+y)$,
\begin{align*}
    \tilde{\ell}_{\tau_1,\{x,y,y\}}(\tau_2, \{x',y',w'\}; \fullAncestralSplitPartitions(\tau_2,\{x',y',w'\}))
    &\ge      p_{0}  \cdot\log((1+x')^2   (1+w')(1+y')^2) \\
    &\qquad + p_{1}  \cdot\log((1+x')^2   (1-w')(1+y')(1-y')) \\
    &\qquad + p_{2}  \cdot\log((1+x')^2   (1-w')(1+y')(1-y')) \\
    &\qquad + p_{3}  \cdot\log((1+x')^2   (1-w')(1+y')(1-y')) \\
    &\qquad + p_{12} \cdot\log((1+x')^2   (1-w')(1+y')^2) \\
    &\qquad + p_{123}\cdot\log((1+x')^2   (1-w')(1+y')(1-y'))\\
    &\qquad + p_{13} \cdot\log((1+x')^2   (1-w')(1-y')^2) \\
    &\qquad + p_{23} \cdot\log((1+x')^2   (1-w')(1-y')^2),
\end{align*}
otherwise
\begin{align*}
    \tilde{\ell}_{\tau_1,\{x,y,y\}}(\tau_2, \{x',y',w'\}; \fullAncestralSplitPartitions(\tau_2,\{x',y',w'\}))
    &\ge      p_{0}  \cdot\log((1+x')^2    (1+w')(1+y')^2) \\
    &\qquad + p_{1}  \cdot\log((1+x')(1-x')(1-w')(1+y')^2) \\
    &\qquad + p_{2}  \cdot\log((1+x')(1-x')(1-w')(1+y')^2) \\
    &\qquad + p_{3}  \cdot\log((1+x')(1-x')(1-w')(1+y')^2) \\
    &\qquad + p_{12} \cdot\log((1+x')^2    (1-w')(1+y')^2) \\
    &\qquad + p_{123}\cdot\log((1+x')(1-x')(1-w')(1+y')^2)\\
    &\qquad + p_{13} \cdot\log((1-x')^2    (1-w')(1+y')^2) \\
    &\qquad + p_{23} \cdot\log((1-x')^2    (1-w')(1+y')^2).
\end{align*}
Letting
$$
b = p_{1}+p_{2}+p_{3}+p_{123}
$$
yields
\begin{align*}
    \tilde{\ell}_{\tau_1,\{x,y,y\}}(\tau_2, \{x',y',w'\}; \fullAncestralSplitPartitions(\tau_2,\{x',y',w'\}))
    &\ge      2\cdot\log(1+x') \\
    &\qquad + (2-b)  \cdot\log(1+y') \\
    &\qquad + b      \cdot\log(1-y') \\
    &\qquad + p_{0}\cdot\log(1+w') \\
    &\qquad + (1-p_{0})\cdot\log(1-w')
\end{align*}
for the first lower bound, but, upon maximizing, we obtain the same value for both cases, namely
\begin{align*}
    \tilde{\ell}_{\tau_1,\{x,y,y\}}(\tau_2, \{x',y',w'\}; \fullAncestralSplitPartitions(\tau_2,\{x',y',w'\}))
    &\ge      2\cdot\log(2) \\
    &\qquad + (2-b)  \cdot\log(2-b) \\
    &\qquad + b      \cdot\log(b) \\
    &\qquad + p_{0}\cdot\log(2p_{0}) \\
    &\qquad + (1-p_{0})\cdot\log(2(1-p_{0}))
\end{align*}
maximized at $\{1,1-b,1-2p_{0}\}$.
Our lower bound is
\begin{align*}
    L_{\tau_1,\tau_2}(\mathbf{p}_{xy}) &:= \shannonDivergence_{\tau_1,\{x,y,y\}}(\tau_2,\{1,1-b,1-2p_{0}\}) \\
                                           &+ 2\cdot\log(2) + (2-b)  \cdot\log(2-b) + b      \cdot\log(b) + p_{0}\cdot\log(2p_{0}) + (1-p_{0})\cdot\log(2(1-p_{0})).
\end{align*}

@@

We want the region where
$$
L_{\tau_1,\tau_2}(\mathbf{p}_{xy}) \ge \max(L^{1}_{\tau_1,\tau_1}(\mathbf{p}_{xy}), L^{2}_{\tau_1,\tau_1}(\mathbf{p}_{xy}),L^{3}_{\tau_1,\tau_1}(\mathbf{p}_{xy})).
$$
Since this is an inequality in two variables, we can plot them analytically---see Fig.~\ref{fig:inconsistency-farris}.

@@

\input{appendix}
